%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{\Large Santosh Kumar Mohanty} % Your name
\address{\small FULL STACK DEVELOPER $\vert$ Node.js $\vert$ AWS $\vert$ React.js } % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\small +91 962 055 3334 $\Vert$ santosh.rit@gmail.com $\Vert$  www.linkedin.com/in/santosh-webdev}  % Your phone number and email


\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{Career Summary}

{\small Experienced Full Stack Developer with a vast array of knowledge in backend, frontend, databases, cloud and best code practices committed to maintaining cutting edge technical skills and up-to-date industry knowledge. My objective is to be the best web developer and a Solutions Architect going forward to contribute to the technology industry all that I know and can do. I am dedicated to perfecting my craft by learning from more seasoned developers, and continuously making strides to learn all that I can about development.}


\end{rSection}
%----------------------------------------------------------------------------------------

%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience \& Projects}

\begin{rSubsection}{Software Development Engineer III $\Vert$ Time Inc.}{August 2014 - Current}{Node.js $\vert$ React.js $\vert$ DynamoDB $\vert$ Elastic Search $\vert$ DevOps }{}
{\small
{\bf Integrated Ad Products }

\item Developed web applications that increases revenue and traffic to the Time Inc brand websites.
\item Developed various products such as photo uploader, polls and quizzes and live blog.
\item Developed highly scalable and low latency Node.js APIs that can handle the entire traffic for Ad Products.
\item Worked in building a generic cross platform/project Authorization/Authentication Module in Node.js used to access different products in Ad Products Platform.
\item Developed modular front-end widgets in React.js that can be imported as a library to any websites based on plug n play architecture.
\item Worked in a combination of databases like DynamoDB and ElasticSearch in providing scalable and fast APIs.
\item Worked on Continuous Integration, deployment and automation of Build using Circle-CI and Code Pipeline, API Test Cases using Supertest, Mocha and functional test with Selenium and Nightwatch-Cucumber .
\item Developed widget components for TimeInc.'s Integrated Brand Platform ELEMENT.
{\newline}
{\newline}
{\bf Site Search}
\item Developed multi-tenant search platform that can serve all the brands from a single shared system in Node.js.
\item Integrated the Search Application with Google custom search API and later with Elastic Search to get in-house search Data from brand websites.
{\newline}
{\newline}
{\bf Sports Illustrated}
\item Worked as FrontEnd and Drupal Developer for Sports Illustrated and SwimSuit.
\item Worked in building a Live Draft Module for NFL Drafts.
}
%  {\bf Internal Site Search}
\end{rSubsection} 


%------------------------------------------------

\begin{rSubsection}{Software Engineer $\Vert$ Impelsys India Pvt. Ltd.}{January 2013 - August 2014}{PHP $\vert$ Joomla $\vert$ MySql $\vert$ Javascript $\vert$ CodeIgniter}{}
{\small
\item Worked on features for websites including NFPA, American Heart Association etc.
\item Worked on building Citation and Single Sign On Authentication Modules.
}
\end{rSubsection}


\end{rSection} 

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical SKILLS}
{\small
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
BackEnd & Node.js, PHP\\ 
FrontEnd & React.js, HTML, CSS, Javascript, HandleBars, JQuery\\  
Databases & MySql, DynamoDB, Search Database like ElasticSearch \\
AWS &  EB, ECS, EC2, SNS, SES, CDN, S3, Redis, Lambda and SQS etc. \\
Testing Frameworks &  Mocha, Chai, Selenium, Nightwatch, Cucumber \\
Source Control &  GIT, SVN \\
\end{tabular}
}

\end{rSection}
%----------------------------------------------------------------------------------------
% \newpage

%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\small
{\bf B.Tech in Computer Science and Engineering} \hfill {2008 - 2012}
\\ 
Biju Patnaik University of Technology, Odisha. ,  CGPA: 7.6/10.00  

{\bf HSE, Class XII} \hfill { 2007 - 2008}
\\ Binayak Acharya Govt. Science College, Berhampur. 62\%
\\ Council of Higher Secondary Education, Odisha

{\textbf{SSE, Class X}}  \hfill 2005 - 2006\\
DAV Public School, Berhampur, 74\% 
\\ Central Board of Secondary Education, New Delhi
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\
}

\end{rSection}
%----------------------------------------------------------------------------------------

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Awards and Certifications }
{\small
\begin{rSubsection}{Star Performer Award $\Vert$ Time Inc.}{October 2016} {} {} 
\item Star Performer for timely delivering quality product and integrating with brand websites.
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Oracle Certified Professional, Java SE6 Programmer }{july 2012}{} {}
\item
\end{rSubsection}
 }
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Personal Details}
{\small
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Name & Santosh Kumar Mohanty\\ 
Email Id & santosh.rit@gmail.com\\  
Mobile Number & 9620553334 \\
LinkedIn & www.linkedin.com/in/santosh-webdev \\
Present Address &  301, Jeevan Sai Meadows, 13th Cross, Manjunath Layout, Marathahalli, Bangalore. \\
Permanent Address &  Tulasi Nagar 7th Lane, Aska Road, Berhampur, Odisha, 760001.\\
\end{tabular}
}
\end{rSection}

\end{document}
